Appendix

### 2019-07-23 manuscript/appendix.Rmd
horizontal trophic plot

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = TRUE) +
  # facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 2))

>>>>

ggplot(dt_waffle,
       aes(fill=`Trophic State`, values = `value`)) +
  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = FALSE) +
  # facet_wrap(~key, ncol = 1) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
                    shades::delta(-10)) +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(strip.background = element_blank(), 
        rect = element_rect(fill = "transparent"), 
        legend.position = "bottom", 
        title = element_blank(), 
        strip.text = element_text(size = 16), 
        legend.text = element_text(size = 10), 
        legend.key.size = unit(0.5, "line")) + 
  guides(fill = guide_legend(nrow = 1))
